### 2022-11-28 draft.tex
Deploying to gh-pages from @ graciellehigino/ms_range_interactions@d8c7546198bb9888afe23f7790b6b7e9dd3277a6 🚀

\vfill
\textbf{\sffamily Abstract: }\textbf{Background.} Range maps are a
useful tool to describe the spatial distribution of species. However,
they need to be used with caution, as they essentially represent a rough
approximation of a species' suitable habitats. When stacked together,
the resulting communities in each grid cell may not always be realistic,
especially when species interactions are taken into account. Here we
show the extent of the mismatch between range maps, provided by the
International Union for Conservation of Nature (IUCN), and species
interactions data. More precisely, we show that local networks built
from those stacked range maps often yield unrealistic communities, where
species of higher trophic levels are completely disconnected from
primary producers. \textbf{Methodology.} We used the well-described
Serengeti food web of mammals and plants as our case study, and provide
updated range maps for all predators by taking into account food web
structure. We then used occurrence data from the Global Biodiversity
Information Facility (GBIF) to investigate where data is most lacking.
\textbf{Results.} We found that most predator ranges comprised large
areas without any overlapping distribution of their preys. However, many
of these areas contained GBIF occurrences of the predator.
\textbf{Conclusions.} Our results suggest that the mismatch between both
data sources could be due either to the lack of information about
ecological interactions or the geographical occurrence of preys. We
finally discuss general guidelines to help identify defective data among
distributions and interactions data, and we recommend this method as a
valuable way to assess whether the occurrence data that are being used,
even if incomplete, are ecologically accurate.
\vfill

@@

Finding a species in a certain location is like finding an encrypted
message that traveled through time. It carries the species' evolutionary
history, migration patterns, as well as any direct and indirect effects
generated by other species (some of which we may not even know exist).
Ecologists have been trying to decode this message with progressively
more powerful tools, from their field notes to highly complex
computational algorithms. However, to succeed in this challenge it is
important to have the right clues in hand. There are many ways we can be
misled by data - or the lack of it: taxonomic errors (e.g., due to
updates in the taxonomy of a species), geographic inaccuracy (e.g.,
approximate coordinates or lack of documentation about their accuracy),
or sampling biases (e.g.~data clustered near roads or research centers)
(Ladle and Hortal 2013; Hortal et al. 2015; Poisot et al. 2021). One way
to identify - and potentially fix - these errors is to combine many
different pieces of information about the occurrence of a species, so
agreements and mismatches can emerge. Although previous studies have
combined different types of occurrence data to measure the accuracy of
datasets (Hurlbert and Jetz 2007; Hurlbert and White 2005; Ficetola et
al. 2014), none have used different types of information so far (i.e.,
ecological characteristics other than geographical distribution). Here
we suggest jointly analysing species occurrence (range maps and point
occurrences) and ecological interactions to identify mismatches between
datasets and areas of data deficit.

@@

It has been demonstrated that the agreement between range maps and point
data varies geographically (Hurlbert and Jetz 2007; Hurlbert and White
2005; Ficetola et al. 2014). Adding ecological interaction data to this
comparison might help to elucidate where these (dis)agreements are more
likely to be true and which dataset better represent the actual
distribution of a species. In this context, we elaborate a method that
allows us to detect areas of potential misestimation of species'
distribution data (more precisely range maps) based on interaction data.
This method is based on the assumption that organisms cannot persist in
an area unless they are directly or indirectly connected to a primary
producer within their associated food web (Power 1992). Thus, given that
herbivores are the main connection between plant resources (directly
limited by environmental conditions) and predators (Dobson 2009; Scott
et al. 2018), the range of a predator (omnivore or carnivore) depends on
the overlapping ranges of its herbivore preys. If sections of a
predator's range does not overlap with at least one of its prey it will
become disconnected from primary producers, and therefore we would not
expect the predator to occur in this area.

This mismatch can be the result of different mechanisms, like the
misestimation of both the predator's and the preys' ranges (Ladle and
Hortal 2013; Rondinini et al. 2006), taxonomic errors (Isaac, Mallet,
and Mace 2004; Ladle and Hortal 2013), or the lack of information about
trophic links (i.e., the lack of connection between the ranges of a
predator and a primary producer may be due a third species we don't know
is connected to both). Here in this proof of concept, we investigate the
disagreements between available data for species that compose a
well-known foodweb in the African continent, discuss the mechanisms that
can lead to this, and reinforce the importance of open geographically
explicit interaction data.

@@

We indentified areas of data deficits on the ranges of predators based
on a simple rule: we removed any part of a predator's range that did not
intersect with the range of at least one prey herbivore species, which
in turn is directly connected to a primary producer (plants). To do
that, we used a Serengeti food web dataset (Baskerville et al. 2011)
(which comprises carnivores, herbivores, and plants from Tanzania) and
its species ranges from IUCN. Then, we calculated the difference in
range sizes between the original IUCN ranges of predators and those
without the areas where they would be alone, based on species
interaction data. Finally, we added the GBIF occurrence points for the
Serengeti species to investigate whether the results would be different
if we used another source of distribution data.

@@

We calculated the geographical overlap, i.e.~the extent to which
interacting predator and prey species co-occurred across their ranges,
as \(a/(a + c)\), where \(a\) is the number of pixels where predator and
prey cooccur and \(c\) is the number of pixels where only the focal
species occur. This index of geographical overlap can be calculated with
prey or predators as the focal species. Values vary between 0 and 1,
with values closer to 1 indicating that there is a large overlap in the
ranges of the two species and values closer to 0 indicating low
cooccurrence across their ranges. For each predator species, we
calculated its generality to understand whether the level of trophic
specialization (i.e., number of prey items per predator) affects the
extent to which the ranges of the species were altered. One would assume
that predators with a greater number of prey taxa (i.e., a higher
generality) are less likely to have significant changes in their range
as it is more likely that at least one prey species is present across
most of their range.

@@

We then converted the occurrence data into raster format by determining
which pixels had a least one GBIF occurrence. This allowed us to remove
the effect of repeated sampling in some locations. These data were used
to validate the range adjustments made based on species interactions
(see beginning of Methods section). To do so, we calculated the
proportion of GBIF presence pixels occurring within both the original
IUCN species range and the adjusted one. We then compared these
proportions for the predators to verify if the range adjustments removed
locations with GBIF observations, hence likely true habitats.

@@

Mammal species found in the Serengeti food web are widespread in Africa,
especially in grasslands and savannahs (panel \emph{(a)} of
fig.~\ref{fig:richness}). From our analysis, most local networks
(69.07\%) built using the original IUCN range maps had at least one
mammal species with a path to a primary producer (panel \emph{(b)} of
fig.~\ref{fig:richness}), which reinforces that the interactions we
observe in the Serengeti foodweb is representative of the interactions
for these mammals in the whole African continent. On average, local food
webs had almost half of their mammal species disconnected from basal
species (mean = 46.2\%, median = 33.3\%). In addition, 16.6\% of the
networks only had disconnected mammals, and the number of mammal species
varied from 1 to 28, with a mean of 6.7. As expected, the proportion of
carnivores with a path to a primary producer was conditional on the
total number of mammal species in each local network (third panel of
fig.~\ref{fig:richness}).

@@

The proportion of GBIF pixels in revised ranges can only be equal to or
lower than that of the original ranges, as our analysis removes pixels
from the original range and does not add new ones. Rather, the absence
of a difference between the two types of ranges indicates that no pixels
with GBIF observations, hence likely true habitats, were removed by our
analysis. Here this proportion was mostly similar to that of the
original IUCN ranges for most predator species (fig.~\ref{fig:gbif}).
Two species showed no difference in proportion (\emph{Lycaon pictus} and
\emph{Panthera leo}) while four species showed only small differences
(\emph{Crocuta crocuta} lost 0.4\% of the original data overlap;
\emph{Caracal caracal} lost 3.4\%; \emph{Acinonyx jubatus} and
\emph{Panthera pardus} lost 6.2\%). On the other hand, three species,
\emph{Canis aureus}, \emph{Canis mesomelas}, and \emph{Leptailurus
serval} showed very high differences, with overlaps lowered by 100\%,
58.4\%, and 100\% respectively. These last two species are also the only
predators with a single prey in our metaweb. \emph{Canis aureus} has
four preys, but it has one of the smallest ranges in IUCN, which is not
covered by any of its preys. This result reinforces the concern raised
in the literature on the use of IUCN range maps for species that are not
well known (Herkt, Skidmore, and Fahr 2017), demonstrating how small
range species are likely to have their distribution underestimated in
the IUCN database. Additionally, the fact that \emph{Canis aureus} had
such a conspicuous discrepancy between its original IUCN range and those
of its preys, and between GBIF and IUCN data, may indicate a taxonomic
incongruency between the three databases used here, which we explore in
the Discussion section. Our results delineate how a mismatch between
GBIF and IUCN databases differ greatly with small changes in herbivore
species ranges, and it is somewhat positively related to range size for
predator species. Moreover, we show that accounting for interactions
does not necessarily aggravates this dissimilarity, but it is relevant
for species about which we have little ecological information or for
specialists groups.

@@

Here we identify areas of data mismatch between species range maps by
using ecological interaction data (predator-prey interactions within
food webs). Our results did show a significant mismatch in the IUCN
range areas of specialized and generalist predatory organisms and their
prey, which highlights the importance of accounting for species
interactions when estimating the range of a species. Although this type
of data mismatch can result of actual ecological processes, outdated
occurrence data, taxonomic errors and more, we argue that, here, they
rather indicate a lack of interaction sampling data.

@@

First, \emph{Panthera leo} was one of the species with no difference
between ranges before and after our analysis, but 50.7\% of its IUCN
range map is not covered by the GBIF occurrences for this species, and
26.4\% of the GBIF point data does not overlap with its IUCN range map
(fig.~\ref{fig:gbif}). In this particular case, the IUCN maps seem to
agree with species interaction data. However, the disagreement between
the IUCN and the GBIF databases is concerning and suggests that the IUCN
maps might overestimate the lion's distribution.

@@

\begin{figure}
\hypertarget{fig:serval}{%
\centering
\includegraphics{figures/serval_mismatch_combined.png}
\caption{Mismatch between serval's range loss and GBIF occurrence of its
prey. The left panel shows the reduction of serval's range when we
consider the IUCN data on its prey. On the right panel, we added GBIF
data on both serval and its prey, with a buffer for the prey to account
for species mobility.}\label{fig:serval}
}
\end{figure}

@@

Here we demonstrated how we can detect areas of data deficit in species
distribution data using ecological interactions. Knowing where
questionable occurrence data are can be crucial in ecological modelling
(Hortal 2008; Ladle and Hortal 2013), and accounting for these errors
can improve model outputs by diminishing the error propagation (Draper
1995). For instance, we believe our method is a way to account for
ecological interactions in habitat suitability models without making the
models more complex, but by making sure (not assuming) that the input
data - the species occurrence - actually accounts for ecological
interactions. Another application of this method is mapping areas where
data are deficient and helping to indicate priority sampling locations
for interaction data, which can, in turn, reduce uncertainty in network
prediction. For example, if a certain pixel confirms the presence of a
species both with IUCN and GBIF data, but lacks connection between
species, this pixel has a high potential to hide an unobserved
interaction and should therefore be a priority sample location.\\
It is important to notice, however, that the quality and usefulness of
this method are highly correlated with the amount and quality of data
available about species' occurrences \textbf{and} interactions. With
this paper, we hope to add to the collective effort to decode the
encrypted message that is the occurrence of a species in space and time.
A promising avenue that adds to our method is the prediction of networks
and interactions in large scales (Strydom et al. 2021; Windsor et al.
2022), for they can add valuable information about ecological
interactions where they are missing. Additionally, in order to achieve a
robust modelling framework towards actual species distribution models we
should invest in efforts to collect and combine open data on species
occurrence and interactions (Windsor et al. 2022), especially because we
may be losing ecological interactions at least as fast as we are losing
species (Valiente-Banuet et al. 2015).

>>>>

\vfill
\textbf{\sffamily Abstract: }\textbf{Background.} Range maps are a
useful tool to describe the spatial distribution of species. However,
they need to be used with caution, as they essentially represent a rough
approximation of a species' suitable habitats. When stacked together,
the resulting communities in each grid cell may not always be realistic,
especially when species interactions are taken into account. Here we
show the extent of the mismatch between range maps, provided by the
International Union for Conservation of Nature (IUCN), and species
interactions data. More precisely, we show that local networks built
from those stacked range maps often yield unrealistic communities, where
species of higher trophic levels are completely disconnected from
primary producers. \textbf{Methodology.} We used the well-described
Serengeti food web of mammals and plants as our case study, and identify
areas of data mismatch within predators' range maps by taking into
account food web structure. We then used occurrence data from the Global
Biodiversity Information Facility (GBIF) to investigate where data is
most lacking. \textbf{Results.} We found that most predator ranges
comprised large areas without any overlapping distribution of their
preys. However, many of these areas contained GBIF occurrences of the
predator. \textbf{Conclusions.} Our results suggest that the mismatch
between both data sources could be due either to the lack of information
about ecological interactions or the geographical occurrence of preys.
We finally discuss general guidelines to help identify defective data
among distributions and interactions data, and we recommend this method
as a valuable way to assess whether the occurrence data that are being
used, even if incomplete, are ecologically accurate.
\vfill

@@

Finding a species in a certain location is like finding an encrypted
message that traveled through time. It carries the species' evolutionary
history, migration patterns, as well as any direct and indirect effects
generated by other species (some of which we may not even know exist).
Ecologists have been trying to decode this message with progressively
more powerful tools, from their field notes to highly complex
computational algorithms. However, to succeed in this challenge it is
important to have the right clues in hand. There are many ways we can be
misled by data - or the lack of it: taxonomic errors (e.g., due to
updates in the taxonomy of a species), geographic inaccuracy (e.g.,
approximate coordinates or lack of documentation about their accuracy),
or sampling biases (e.g., data clustered near roads or research centers)
(Ladle and Hortal 2013; Hortal et al. 2015; Poisot et al. 2021). One way
to identify - and potentially fix - these errors is to combine many
different pieces of information about the occurrence of a species, so
agreements and mismatches can emerge. Although previous studies have
combined different types of occurrence data to measure the accuracy of
datasets (Hurlbert and Jetz 2007; Hurlbert and White 2005; Ficetola et
al. 2014), none have used different types of information so far (i.e.,
ecological characteristics other than geographical distribution). Here
we suggest jointly analysing species occurrence (range maps and point
occurrences) and ecological interactions to identify mismatches between
datasets and areas of data deficit.

@@

It has been demonstrated that the agreement between range maps and point
data varies geographically (Hurlbert and Jetz 2007; Hurlbert and White
2005; Ficetola et al. 2014). Adding ecological interaction data to this
comparison might help to elucidate where these (dis)agreements are more
likely to be true and which dataset better represent the actual
distribution of a species. In this context, we elaborate a method that
allows us to detect areas of potential misestimation of species'
distribution data (more precisely range maps) based on interaction data.
This method is based on the assumption that organisms cannot persist in
an area unless they are directly or indirectly connected to a primary
producer within their associated food web (Power 1992). Thus, given that
herbivores are the main connection between plant resources (directly
limited by environmental conditions) and predators (Dobson 2009; Scott
et al. 2018), the range of a predator (omnivore or carnivore) depends on
the overlapping ranges of its herbivore preys. If sections of a
predator's range do not overlap with at least one of its prey it will
become disconnected from primary producers, and therefore we would not
expect the predator to occur in this area.

This mismatch can be the result of different mechanisms, like the
misestimation of both the predator's and the preys' ranges (Ladle and
Hortal 2013; Rondinini et al. 2006), taxonomic errors (Isaac, Mallet,
and Mace 2004; Ladle and Hortal 2013), or the lack of information about
trophic links (i.e., the lack of connection between the ranges of a
predator and a primary producer may be due a third species we don't know
is connected to both). Here in this proof of concept, we investigate the
disagreements between available data for species that compose a
well-known food web in the African continent, discuss the mechanisms
that can lead to this, and reinforce the importance of open
geographically explicit interaction data.

@@

We identified areas of data deficits within the ranges of predators
based on a simple rule: any part of a predator's range that did not
intersect with the range of at least one prey herbivore species, which
in turn is directly connected to a primary producer (plants), was
considered data deficient. To do that, we used a Serengeti food web
dataset (Baskerville et al. 2011) (which comprises carnivores,
herbivores, and plants from Tanzania) and its species ranges from IUCN.
Then, we calculated the difference in range sizes between the original
IUCN ranges of predators and those without the areas where they would be
disconnected from their food webs, based on species interaction data.
Finally, we added the GBIF occurrence points for the Serengeti species
to investigate whether the results would be different if we used another
source of distribution data.

@@

We calculated the geographical overlap, i.e.~the extent to which
interacting predator and prey species co-occurred across their ranges,
as \(a/(a + c)\), where \(a\) is the number of pixels where predator and
prey cooccur and \(c\) is the number of pixels where only the focal
species occur. This index of geographical overlap can be calculated with
prey or predators as the focal species. Values vary between 0 and 1,
with values closer to 1 indicating that there is a large overlap in the
ranges of the two species and values closer to 0 indicating low
cooccurrence across their ranges. For each predator species, we
calculated its generality to understand whether the level of trophic
specialization (i.e., number of prey items per predator) affects the
extent to which the ranges of the species comprised areas of data
deficits. One would assume that predators with a greater number of prey
taxa (i.e., a higher generality) are less likely to have large areas of
data mismatch within their range as it is more likely that at least one
prey species is present across most of their range.

@@

We then converted the occurrence data into raster format by determining
which pixels had at least one GBIF occurrence. This allowed us to remove
the effect of repeated sampling in some locations. These data were used
to validate the areas identified as being ecologically unrealistic based
on species interactions and occurrence data (see beginning of Methods
section). To do so, we calculated the proportion of GBIF presence pixels
occurring within both the original IUCN species range and the adjusted
one (i.e., the one without unrealistic food webs). We then compared
these proportions for all predators to verify if the areas of data
mismatch contained locations with GBIF observations, hence likely true
habitats.

@@

Mammal species found in the Serengeti food web are widespread in Africa,
especially in grasslands and savannahs (panel \emph{(a)} of
fig.~\ref{fig:richness}). From our analysis, most local networks
(69.07\%) built using the original IUCN range maps had at least one
mammal species with a path to a primary producer (panel \emph{(b)} of
fig.~\ref{fig:richness}), which reinforces that the interactions we
observe in the Serengeti food web is representative of the interactions
for these mammals in the whole African continent. On average, local food
webs had almost half of their mammal species disconnected from basal
species (mean = 46.2\%, median = 33.3\%). In addition, 16.6\% of the
networks only had disconnected mammals, and the number of mammal species
varied from 1 to 28, with a mean of 6.7. As expected, the proportion of
carnivores with a path to a primary producer was conditional on the
total number of mammal species in each local network (third panel of
fig.~\ref{fig:richness}).

@@

The proportion of GBIF pixels in revised ranges can only be equal to or
lower than that of the original ranges, as our analysis removes pixels
from the original range and does not add new ones. Rather, the absence
of a difference between the two types of ranges indicates that no pixels
with GBIF observations, hence likely true habitats, were removed by our
analysis. Here this proportion was mostly similar to that of the
original IUCN ranges for most predator species (fig.~\ref{fig:gbif}).
Two species showed no difference in proportion (\emph{Lycaon pictus} and
\emph{Panthera leo}) while four species showed only small differences
(\emph{Crocuta crocuta} lost 0.4\% of the original data overlap;
\emph{Caracal caracal} lost 3.4\%; \emph{Acinonyx jubatus} and
\emph{Panthera pardus} lost 6.2\%).

On the other hand, three species, \emph{Canis aureus}, \emph{Canis
mesomelas}, and \emph{Leptailurus serval} showed very high differences,
with overlaps lowered by 100\%, 58.4\%, and 100\% respectively. These
last two species are also the only predators with a single prey in our
metaweb. \emph{Canis aureus} has four preys, but it has one of the
smallest ranges in IUCN, which is not covered by any of its preys. This
result reinforces the concern raised in the literature on the use of
IUCN range maps for species that are not well known (Herkt, Skidmore,
and Fahr 2017), demonstrating how small range species are likely to have
their distribution underestimated in the IUCN database. Additionally,
the fact that \emph{Canis aureus} had such a conspicuous discrepancy
between its original IUCN range and those of its preys, and between GBIF
and IUCN data, may indicate a taxonomic incongruency between the three
databases used here, which we explore in the Discussion section. Our
results delineate how a mismatch between GBIF and IUCN databases differ
greatly with small changes in herbivore species ranges, and it is
somewhat positively related to range size for predator species.
Moreover, we show that accounting for interactions does not necessarily
aggravates this dissimilarity, but it is relevant for species about
which we have little ecological information or for specialists groups.

@@

Here we identify areas of data mismatch between species range maps by
using ecological interaction data (predator-prey interactions within
food webs). Our results did show a significant mismatch in the IUCN
range areas of specialized and generalist predatory organisms and their
prey, which highlights the importance of accounting for species
interactions when estimating the range of a species. Although this type
of data mismatch can be result of actual ecological processes, outdated
occurrence data, taxonomic errors and more, we argue that, here, they
rather indicate a lack of interaction sampling data.

@@

First, \emph{Panthera leo} was one of the species with no difference
between ranges before and after our analysis, but 50.7\% of its GBIF
pixels did not superpose with the IUCN range (fig.~\ref{fig:gbif}). In
this particular case, the IUCN maps seem to agree with species
interaction data. However, the disagreement between the IUCN and the
GBIF databases is concerning and suggests that the IUCN maps might
underestimate the lion's distribution.

@@

\begin{figure}
\hypertarget{fig:serval}{%
\centering
\includegraphics{figures/serval_mismatch_combined.png}
\caption{Mismatch between servals' range loss and GBIF occurrence of its
prey. The left panel shows the reduction of servals' range when we
consider the IUCN data of its prey. On the right panel, we added GBIF
data on both serval and its prey, with a buffer for the prey to account
for species mobility.}\label{fig:serval}
}
\end{figure}

@@

Here we demonstrated how we can detect areas of data deficit in species
distribution data using ecological interactions. Knowing where
questionable occurrence data are can be crucial in ecological modelling
(Hortal 2008; Ladle and Hortal 2013), and accounting for these errors
can improve model outputs by diminishing the error propagation (Draper
1995). For instance, we believe our method is a way to account for
ecological interactions in habitat suitability models without making the
models more complex, but by making sure (not assuming) that the input
data - the species occurrence - actually accounts for ecological
interactions. Another application of this method is mapping areas where
data are deficient, thus helping to identify priority sampling locations
for interaction data, which can, in turn, reduce uncertainty in network
prediction. For example, if a certain pixel confirms the presence of a
species both with IUCN and GBIF data, but lacks connection between
species, this pixel has a high potential to hide an unobserved
interaction and should therefore be a priority sampling location.\\
It is important to notice, however, that the quality and usefulness of
this method are highly correlated with the amount and quality of data
available about species' occurrences \textbf{and} interactions. With
this paper, we hope to add to the collective effort to decode the
encrypted message that is the occurrence of a species in space and time.
A promising avenue that adds to our method is the prediction of networks
and interactions at large scales (Strydom et al. 2021; Windsor et al.
2022), for they can add valuable information about ecological
interactions where they are missing. Additionally, in order to achieve a
robust modelling framework towards actual species distribution models we
should invest in efforts to collect and combine open data on species
occurrence and interactions (Windsor et al. 2022), especially because we
may be losing ecological interactions at least as fast as we are losing
species (Valiente-Banuet et al. 2015).

### 2022-11-28 preprint.tex
Deploying to gh-pages from @ graciellehigino/ms_range_interactions@d8c7546198bb9888afe23f7790b6b7e9dd3277a6 🚀

\textbf{Abstract}:\,\textbf{Background.} Range maps are a useful tool to
describe the spatial distribution of species. However, they need to be
used with caution, as they essentially represent a rough approximation
of a species' suitable habitats. When stacked together, the resulting
communities in each grid cell may not always be realistic, especially
when species interactions are taken into account. Here we show the
extent of the mismatch between range maps, provided by the International
Union for Conservation of Nature (IUCN), and species interactions data.
More precisely, we show that local networks built from those stacked
range maps often yield unrealistic communities, where species of higher
trophic levels are completely disconnected from primary producers.
\textbf{Methodology.} We used the well-described Serengeti food web of
mammals and plants as our case study, and provide updated range maps for
all predators by taking into account food web structure. We then used
occurrence data from the Global Biodiversity Information Facility (GBIF)
to investigate where data is most lacking. \textbf{Results.} We found
that most predator ranges comprised large areas without any overlapping
distribution of their preys. However, many of these areas contained GBIF
occurrences of the predator. \textbf{Conclusions.} Our results suggest
that the mismatch between both data sources could be due either to the
lack of information about ecological interactions or the geographical
occurrence of preys. We finally discuss general guidelines to help
identify defective data among distributions and interactions data, and
we recommend this method as a valuable way to assess whether the
occurrence data that are being used, even if incomplete, are
ecologically accurate.

>>>>

\textbf{Abstract}:\,\textbf{Background.} Range maps are a useful tool to
describe the spatial distribution of species. However, they need to be
used with caution, as they essentially represent a rough approximation
of a species' suitable habitats. When stacked together, the resulting
communities in each grid cell may not always be realistic, especially
when species interactions are taken into account. Here we show the
extent of the mismatch between range maps, provided by the International
Union for Conservation of Nature (IUCN), and species interactions data.
More precisely, we show that local networks built from those stacked
range maps often yield unrealistic communities, where species of higher
trophic levels are completely disconnected from primary producers.
\textbf{Methodology.} We used the well-described Serengeti food web of
mammals and plants as our case study, and identify areas of data
mismatch within predators' range maps by taking into account food web
structure. We then used occurrence data from the Global Biodiversity
Information Facility (GBIF) to investigate where data is most lacking.
\textbf{Results.} We found that most predator ranges comprised large
areas without any overlapping distribution of their preys. However, many
of these areas contained GBIF occurrences of the predator.
\textbf{Conclusions.} Our results suggest that the mismatch between both
data sources could be due either to the lack of information about
ecological interactions or the geographical occurrence of preys. We
finally discuss general guidelines to help identify defective data among
distributions and interactions data, and we recommend this method as a
valuable way to assess whether the occurrence data that are being used,
even if incomplete, are ecologically accurate.
